True versus apparent shapes of astrophysical bow shocks

### 2016-02-05 papers/Paper1/sec-application.tex
Advance in section 5 writing.

We measured the Characteristic radii in Orion Nebula proplyds from observations with the ACS camera from the Hubble Space Telescope (HST) using a lamp filter around $\lambda = 5007 \AA$. The observations

@@

Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta_1^C$. We followed the brightness contours along the 
bow shocks to mark the shell's position. In order to obtain the set of measurements $(R_0, R_c, D)$, we moved to the proplyd's reference frame, (where the proplyd's position)
is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions. The figure ()
shows a representation of the metodology described.

\input{proplyds-table}
%\begin{figure}
%\end{figure}

>>>>

We measured the Characteristic radii in Orion Nebula proplyds from observations with the ACS camera from the Hubble Space Telescope (HST) using a lamp filter around $\lambda = 5007 \AA$. The proposal for these observations were done by  Jogee, S. in 2004 with calibration purposes but (he never published anything using expliciyly these observations). % We must check if this phrase should be included
Neverthless, as we are only interested in measure the geometric shape of bow shocks, these observations are more than enough.

@@

Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta_1^C$. We followed the brightness contours along the 
bow shocks to mark the shell's position. In order to obtain the set of measurements $(R_0, R_c, D)$, we moved to the proplyd's reference frame, (where the proplyd's position)
is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions. The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described. Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lessim theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$. Instead, we introduced the radius of curvature after we realized how well the shell's marks fits into a circle for all the proplyds (see figure ()).

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV3} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV3} \\
\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV4} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV4}
\end{tabular}
\end{figure*}

\begin{figure}
\includegraphics[width=\linewidth]{177-341-will-anota}
\caption{Schematic example of the observational measures used. We don't use $R_\theta$ any longer, but instead the radius of curvature}
\label{fig:radii-measures-example}
\end{figure}

\input{proplyds-table}

%\begin{figure}
%\end{figure}
